---
title: "spia"
output: html_document
---

##Read in dataset
```{r message = FALSE}
library(SPIA)
dataset_file = '/Users/karthik/Documents/bioinformatics_tsri/spia/pnas.csv'
dataset = read.csv(dataset_file, as.is=T, header=T)
```

##Subset genes with log fold chagne > 0.6 and P value <= 0.05
```{r}
gene_list <- dataset$BPA > 0.6 & dataset$P.value <= 0.05
subset <- dataset[gene_list,]
```

#SPIA
```{r}
tmp <- subset$BPA
names(tmp) <- subset$EntrezGene
res = spia(de=tmp, all=names(tmp), organism="mmu")
dim(res)
head(res)
```

##map2pathway function
```{r}
map2pathway = function(id.list, scopes='entrezgene', pathway.src="kegg", sep=', '){
  pw.field = paste('pathway', pathway.src, sep=".")
  res = queryMany(id.list, scopes=scopes, fields=pw.field)
  format.pathway = function(one.res){
    id = one.res$query
    if (!is.null(one.res[[pw.field]])){
      pw.names = paste(one.res[[pw.field]]$name, collapse=sep)
      pw.ids = paste(one.res[[pw.field]]$id, collapse=sep)
      return(c(id, pw.ids, pw.names))
    }else{
      return(c(id, NA, NA))
    }
  }
 out = apply(as.data.frame(res), 1, format.pathway)
 out = t(out)
 colnames(out) <- c('id', paste(pathway.src, '.id', sep=''), paste(pathway.src, '.name', sep=''))
 return(out)
}
```

```{r message = FALSE}
library(mygene)
```
```{r}
p <- map2pathway(names(tmp), sep='<br>')
p <- na.omit(p)
dim(p)
head(p)
```

